### 2020-05-13 probabilisticProgrammingMartingales.tex
Added diagram.

@@

With this notation, a more general reduction relation $\to$ can be defined. \akr{It would almost work to have one of the neater versions of $\tY$-reduction here.}
\lo{On first reading, I struggled to parse the following clauses.}
\changed[lo]{The binary relation $\to$ is defined by the following rules, each is conditional on a position $P$ that occurs in the term $M$ in question.}
\begin{align*}
  \text{if } M \mid P = (\lambda x.s) v,\ & M \to M[s[v/x]/P] \\
  \text{if } M \mid P = \underline f (\underline r_1, \dots , \underline r_n),\ & M \to M[\underline{f(r_1,\dots,r_n)}/P] \\
  \text{if } M \mid P = \tY \lambda x. s,\ & M \to M[\lambda z. s[(\tY \lambda x. s)/x] z/P] \text{ where $z$ is not free in $s$}\\
  \text{if } M \mid P = \tif{\underline r < 0}{s_1}{s_2},\ & M \to M[s_1/P] \text{ where }r < 0 \\
  \text{if } M \mid P = \tif{\underline r < 0}{s_1}{s_2},\ & M \to M[s_2/P] \text{ where }r \geq 0 \\
  \text{if } M \mid P = \tsample & \text{ and $\lambda$ does not occur after $@_2$ or $\tY$ in $P$},\\ & M \to M[\underline r/P] \text{ where } r \in [0,1] \\
  \text{if } M \mid P = \tscore(\underline r),\ & M \to M[\underline r/P].
\end{align*}
\lo{The definition above is clear. But as a general rule, it is good to illustrate definitions -- especially if they are genuinely new -- with an example or two.}

@@

Given a closed term $M$, let $L_0(M)$ be the set of pairs, the first element of which is a reduction sequence starting at $M$, and the second of which is a position in the final term of the reduction sequence. Reduction sequences are used rather than reachable terms because if the same term is reached twice, different samples may be needed, but they will be discussed as though they were terms, by abuse of notation. \lo{Readers would benefit greatly from some examples of an $L_0(M)$-pair, and relations $\sim_p$ and $\sim_c$, here, before the formal definitions. Explain the underlying intuition.} The relation $\sim$ is defined as the union of the symmetric relations $\sim_p$ and $\sim_c$ where
\begin{enumerate}
    \item If $N$ reduces to $O$ with the redex at position $P$\lo{Do you mean: $M \to^\ast N \to O = N[\dotDelta / P]$ for some redex contraction $\Delta \to \dotDelta$}, and $Q$ is a position in $N$ 
    where $Q \not \geq P$, then $(N,Q) \sim_p (O,Q)$.
    \lo{This implies that $Q$ is a position in $O$, but $O \mid Q$ is not guaranteed to exist. E.g.~$N = (\lambda x.x) 1$ and $O = 1$. Now $N \mid Q$ exists, where $Q = @_1 ; \lambda$, but $O \mid Q$ does not exist.}

@@

>>>>

\usepackage{graphicx}

@@

With this notation, a more general reduction relation $\to$ can be defined. \akr{It would almost work to have one of the neater versions of $\tY$-reduction here.}
\lo{On first reading, I struggled to parse the following clauses.}
\changed[lo]{The binary relation $\to$ is defined by the following rules, each is conditional on a redex occuring at position $P$ in the term $M$ in question.}
\begin{align*}
  \text{if } M \mid P = (\lambda x.s) v,\ & M \to M[s[v/x]/P] \\
  \text{if } M \mid P = \underline f (\underline r_1, \dots , \underline r_n),\ & M \to M[\underline{f(r_1,\dots,r_n)}/P] \\
  \text{if } M \mid P = \tY \lambda x. s,\ & M \to M[\lambda z. s[(\tY \lambda x. s)/x] z/P] \text{ where $z$ is not free in $s$}\\
  \text{if } M \mid P = \tif{\underline r < 0}{s_1}{s_2},\ & M \to M[s_1/P] \text{ where }r < 0 \\
  \text{if } M \mid P = \tif{\underline r < 0}{s_1}{s_2},\ & M \to M[s_2/P] \text{ where }r \geq 0 \\
  \text{if } M \mid P = \tsample & \text{ and $\lambda$ does not occur after $@_2$ or $\tY$ in $P$},\\ & M \to M[\underline r/P] \text{ where } r \in [0,1] \\
  \text{if } M \mid P = \tscore(\underline r),\ & M \to M[\underline r/P].
\end{align*}
\lo{The definition above is clear. But as a general rule, it is good to illustrate definitions -- especially if they are genuinely new -- with an example or two.}

@@

Given a closed term $M$, let $L_0(M)$ be the set of pairs, the first element of which is a reduction sequence starting at $M$, and the second of which is a position in the final term of the reduction sequence. Reduction sequences are used rather than reachable terms because if the same term is reached twice, different samples may be needed, but they will be discussed as though they were terms, by abuse of notation. \lo{Readers would benefit greatly from some examples of an $L_0(M)$-pair, and relations $\sim_p$ and $\sim_c$, here, before the formal definitions. Explain the underlying intuition.} The relation $\sim$ is defined as the union of the symmetric relations $\sim_p$ and $\sim_c$ where
\begin{enumerate}
    \item If $N$ reduces to $O$ with the redex at position $P$\lo{Do you mean: $M \to^\ast N \to O = N[\dotDelta / P]$ for some redex contraction $\Delta \to \dotDelta$}, and $Q$ is a position in $N$ 
    where $Q \not \geq P$, then $(N,Q) \sim_p (O,Q)$.
    \lo{This implies that $Q$ is a position in $O$, but $O \mid Q$ is not guaranteed to exist. E.g.~$N = (\lambda x.x) 1$ and $O = 1$. Now $N \mid Q$ exists, where $Q = @_1 ; \lambda$, but $O \mid Q$ does not exist.}
    \lo{Ah! I overlooked the condition $Q \not\geq P =
    {\cdot}$.}

@@

\begin{figure}
\includegraphics[height=0.9\textheight]{akr-diagram.pdf}
\caption{\label{fig:adk-diagram} Some examples of $\sim_p$- and $\sim_c$-rules}
\end{figure}

\begin{example}
See \Cref{fig:adk-diagram} for examples of $\sim_p$- and $\sim_c$-rules.
\end{example}
